\documentclass[letterpaper]{article}
\usepackage[dvipsnames]{xcolor}
\usepackage[margin=0.75in]{geometry}
\usepackage{relsize}
\usepackage{multicol}
\usepackage{mdwlist}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\pagestyle{empty}
\newcommand*\titleResume[3]{\vbox to 0pt{\hfill\scriptsize\color{gray}{#3}}\vspace{-0.4em}\noindent{\LARGE\textbf{#1}}\ \ \ \emph{#2}}
\newcommand*\bull{ \  \ $\cdot$\  \ }
\newcommand*\roottitle[1]{\subsection*{#1}}
\newcommand*\horizontalrule[2]{\vspace{#1}{\hrule}\vspace{#2}}
\newcommand*\headedSection[3]{\begin{indentpar}{15pt}\item[]\textscale{1.1}{#1}\hfill\textsc{#2}{#3}\end{indentpar}}
\newcommand*\headedSabSection[2]{\begin{indentpar}{15pt}\item[]\textbf{#1}\hfill\emph{#2}\end{indentpar}}
\newcommand*\body[1]{\begin{indentpar}{45pt}\item[]{#1}\end{indentpar}}
\newcommand*\inlineHeadedSection[2]{\begin{basedescript}{\setlength{\leftmargin}{30pt}}\item[\hspace{15pt}\textbf{#1}]{#2}\end{basedescript}}
\newenvironment{indentpar}[1]{
\begin{list}{}{\setlength{\leftmargin}{#1}\setlength{\parsep}{0pt}\setlength{\parskip}{0pt}\setlength{\itemsep}{0pt}\setlength{\topsep}{0pt}}}{\end{list}}
\begin{document}
\titleResume{Jonny Wilson}{August 25 1987}{Last updated \today}
\\
\noindent jonnylwilson@gmail.com\bull (469)269-9378\bull www.linkedin.com/in/jonnylwilson
\\
\noindent Seattle, WA\bull 98121
\horizontalrule{0.4em}{-0.4em}
\roottitle{Summary}
\begin{multicols}{2}
{\noindent\emph{Performance driven engineer with 10 years’ expertise, in the
design, development, software and commissioning of industrial
control systems. With a speciality in material handling and conveyor control systems.}
\\
\\
With over a 150 successfully completed projects
spanning the, municipal, food \& beverage, automotive, milling, and marine
industries. Skilled in the ability to troubleshoot, debug, and support
manufacturing machinery.

Has a genuine interest to further his knowledge and improve
understanding of processes to achieve the best possible result.}
\end{multicols}
\horizontalrule{-0.3em}{-0.4em}
\roottitle{Experience}
\headedSection{Systems Interface Inc.}{Washington, USA}
{\headedSabSection{Senior Project Engineer}{Jul '14 - Present}}
\body{Responsible for all phases of automation engineering; Control panel
electrical mechanical design, PLC \& HMI Programming, drafting, device
specification, project commissioning, customer training, support and service.
Manage all aspects of projects including scheduling, trade coordination, and
customer communication. Mentoring and Management a team of
engineers. Notable projects include: 2\textsuperscript{nd} largest Apple palletizer system in the U.S, 56-Lane High speed sortation systems for a major clothing distributor, 30+ conveyor systems for various craft brewery's.}
\headedSection{Eltech Electric Inc}{Washington, USA}
{\headedSabSection{Electrical Control Systems Engineer}{Jan '14 - Jul '14}}
\body{Working with RSlogix5000 and Factory Talk View Studio; design and development of AMS,
 generator control systems, and brewing control systems, using
various protocols including Modbus, CAN bus, and Ethernet IP to communicate to
proprietary equipment.}
\headedSection{PK Electrical Ltd}{Carlisle, UK}
{\headedSabSection{Electrical Controls Systems Engineer}{Jan '09 - Jan '14}}
\body{Design and Implement Industrial Control systems for the Food and
Beverage,automotive and milling industries, using Allen Bradley, Siemens and
Mitsubishi PLC and HMI’s, utilizing various communications including; Ethernet
IP, Profibus, ControlNet, DeviceNet, and AS-I Bus.}
\horizontalrule{1em}{-0.4em}
\roottitle{Education}
\headedSection{Carlisle College}{Carlisle, UK}
{\headedSabSection{BEng Industrial Instrumentation and Control Engineering }{2006 - 2009}}
\body{Studies focused on Industrial programming languages and
principles.Ladderlogic, Statement List, Pascal, Visual Programming (Labview).
Simulation using Matlab.}
\horizontalrule{1em}{-0.4em}
\roottitle{Skills}
\inlineHeadedSection{Technical Expertise:}
{Expert in Ladderlogic,and Statement list PLC programming. Development of
modular, re-usable, maintainable code. Proficient in AutoCAD(custom lisps and
scripting) and Eplan P8 Electrical. Solid knowledge of web technologies
(HTML/CSS), expert in advanced networking configuration, barcode scanner/imager configuration, vision systems, SQL database development, knowledge of various print \& apply engines, TCP/IP socket 
communications, Modbus (TCP/IP \& RTU), VPN configuration. }
\horizontalrule{0em}{-0.4em}
\roottitle{Interests}
\inlineHeadedSection{Non exhaustive and in alphabetical order:}
{Hiking, music, open source, Running, software development, Travelling, Unix, Vim.}
\end{document}
